---
title: "Seat Clumping"
author: "Niel Schrage"
date: "2/12/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(reprex)
library(ggplot2)
```

## Decision Making

do people clump by gender?
how do you measure that? 
how to deal with grad students?

how would you measure a success case? 
compare against 50% / 50%
compare sample v. reality to “idealized world”
sufficient statistic for measurement clumping…

doing 1000 samples and then comparing the our sample mean against it
3/7 are clumped → is that a good representation
2/7 are equal → is that a good representation


 

### Visual Representation of the Class

M: 14, F: 16

MMFF

MMFF

MMFF

MMFF

MMFF

MMFF

MMFF

FF



```{r simulation, echo = FALSE}

# make sure we get same result as one we made conclusions on

set.seed(31)

# running 1000 simulations

n_sims <- 1000
n_tables <- rep(NA, n_sims)

for (s in 1:n_sims) {

  # creating a vector of 30 students, we are not including grad students

  vector <- (1:30)

  # this is the split of the class. Creates a vector of 30 values

  genders <- c(rep("M", 14), rep("F", 16))

  # creating a dataframe to make our calculations. We included the sample function to get random seat assignment

  x <- data.frame(vector, genders, sample(1:30, 30, replace = F))
  colnames(x) <- c("student", "genders", "seat")


  x <- x %>%

    # our nifty way to group students by table. So if you have a seat number 1-4, you are put into table 1.

    mutate(table = ceiling(seat / 4)) %>%
    group_by(table) %>%

    # count of how many males and females are in each table.

    count(genders) %>%

    # excluding table 8 because there are only 2 students there. 6 grad students mess everything up

    filter(table != 8) %>%

    # even tables.

    filter(genders == "M" & n == 2) %>%
    nrow()

  n_tables[s] <- x
}
```


```{r histogram, echo=FALSE}

n_tables_graph <- as.data.frame(n_tables)

n_tables_graph %>%
  ggplot() +
  geom_histogram(aes(x = n_tables), bins = 8) +
  labs(
    title = "Simulated Distribution of Tables with Even Gender Split",
    subtitle = "Red = Simulated Mean, Blue = Observed Mean",
    caption = "David Kane, Gov 1006, February 12",
    x = "Number of Tables",
    y = "Count"
  ) +

  geom_vline(aes(xintercept = mean(n_tables)), color = "red", linetype = "dashed", size = .5) +

  geom_vline(aes(xintercept = 2), color = "blue", linetype = "dashed", size = .5) +

  theme_light()
```

This histogram shows us that the number of equal tables (we defined as having 2M and 2F) we observed in class (2/7) is not an unlikely value. After running 1000 simulations of the class, and looking to see what the number of equal tables across the distribution was slightly below 3. 
This histogram looks to be approximately normal... After looking at the data, we believe that the students in Gov 1006 

If we were to continue looking at this information, we would try to look at the tables that were completely male or female, because we know how many are even -- but we don't know about the others. Are they all female/all male or is there a 3-1 mix. 
